\documentclass[12pt]{../sdsmt-thesis/thesis}

%% The default font is Computer Modern Roman for text and math. Uncomment
%% one of the following to choose a different font set.
% \usepackage{mathptmx} % Times New Roman with math fonts
% \usepackage{newcent}  % new century schoolbook font
% \usepackage{bookman}  % bookman font
% \usepackage{fourier}  % Utopia (text) and Fourier (math) font
% \usepackage{times}
% \usepackage{mathptm}

\input{../research.sty}
\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}

\newcommand{\subfilefrontmatter}{\maketitle\preliminaries{}\tableofcontents\body{}}
\newcommand{\subfilebackmatter}{\supplementaries{}\bibliography{bibliography}}

%% Uncomment the following two lines and comment out the third one
%% if you want to use the Chicago Manual based bibliography.
% \usepackage{thesiscitations}
% \bibliographystyle{thesis}
\bibliographystyle{ieeetr}

%% Uncomment next line to print a double-spaced draft version
% \dsdraft

%% Uncomment next line to print a single-spaced draft version
\ssdraft{}

\doctype{thesis}

%% TODO: Find a title.
\title{Something About Haiku}
\author{Austin Gill}
\degree{Master of Science in Computational Sciences and Robotics}
\defensedate{\FIXME{May 42, 2020}}
\gradyear{2020}
\department{Computer Science and Engineering}

% The following commands add a signature line for each person who needs
% to sign the thesis/dissertation
\signatureline{Major Professor --- Christer Karlsson, Ph.D., Department of Computer Science and Engineering}
\signatureline{Graduate Division Representative --- Rodney Rice, Ph.D., Department of Humanities}
\signatureline{Committee Member --- Karen Braman, Ph.D., Department of Mathematics}
\signatureline{Head of the Computer Science and Engineering Department --- Jeff McGough, Ph.D.}
\signatureline{Dean of Graduate Education --- Maribeth Price, Ph.D.}

\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\maketitle

%% Comment the next line to remove the copyright notice.  Read the
%% section on copyright in the Thesis and Dissertation Writing
%% Instructions. The copyright must go BEFORE \preliminaries
\makecopyright{}
\preliminaries{}

\begin{abstract}
    \TODO{Add an abstract eventually}
\end{abstract}

\begin{acknowledgments}
    \TODO{Add acknowledgments eventually}
\end{acknowledgments}

\tableofcontents
\listoftables
\listoffigures

\begin{preface}
    \TODO{Add preface}
\end{preface}

%% End of \preliminaries.
\body{}

\subfile{chapters/introduction.tex}
\subfile{chapters/methodology.tex}
\subfile{chapters/results.tex}
\subfile{chapters/conclusions.tex}

%% End of \body.
\supplementaries{}
\bibliography{bibliography}

\begin{appendices}
    \appendix{Appendix A}
    \TODO{Come up with a good way to convert notebooks to \LaTeX{} and include them here.}
\end{appendices}

\begin{vita}
    Format the vita page according to the following graduate school requirements:

    A vita page, not over one page in length, is to be included as the
    last page of all theses and dissertations deposited in the Devereaux
    Library. The vita is to be written in the third person using
    professional style and could contain the following information
    (although you may wish to omit A and B if concerned about identity
    theft):
    \begin{enumerate}[label=\Alph*.]
        \item Place and date of birth.
        \item Place and date of high school graduation.
        \item Place and date of college graduation—with degree and major.
        \item Place and date of receipt of master’s degree—with major.
        \item Vocational and professional experience (not summer jobs)—including dates, nature of position, and school or organization.
        \item Military experience, with indication of professional relevance—if any.
        \item Scholarly publications, exhibits of creative work, membership in professional organizations and honorary societies.
    \end{enumerate}
    \TODO{Add vita}
\end{vita}

\end{document}
