% !TEX root = ../notes.tex
\section{Introduction}\label{sec:introduction}

Throughout these notes, vocabulary items will be typeset in
\textbf{\textcolor{__glossary_entry_color}{bold blue}} letters, and will link
to the~\nameref{glos:main}. Acronyms can be found at \nameref{glos:acronym}.

\subsection{General Research Question}\label{sec:research-question}

This will take some serious refinement, but for now, my research question is

\begin{quote}
    Is it possible to generate believable poetry without falling back to a simple template or
    rule-based system? What techniques in deep learning\todo{Add glossary entry} or \gls{NLP} might
    be employable?
\end{quote}

I will also have to decide if I want to focus on haikus (I think I should at the moment) or some
other form of poetry. Shakespearean sonnets, for example, might be easier because they are longer,
and the training dataset is better defined and easier to get a hold of.

\subsection{Techniques to Explore}\label{sec:techniques-to-explore}

I have already attempted to generate haikus using a naive LSTM\todo{Add glossary entry} generative
deep learning model. I did not have much success, but that may have been due to the limited size of
my training dataset.

The problem with the LSTM generative model is that it is completely unaware that it is generating
\textit{natural language}. So we are, in effect, not using all of the information available. That
is, haikus follow (loosely) the usual rules of English grammar. This means that it may be possible
to supplement the LSTM model using \gls{NLP} techniques.

I am currently taking a course in Natural Computing\todo{Add glossary entry}, which excels in areas
where the problem is subtle and complex. Further, it is possible in natural computing to run an
algorithm without an explicit fitness function; all that's necessary is a comparative process where
one individual is compared to another. This could be crowdsourced via a website.

One of the most promising techniques that I have learned so far is grammatical evolution via an
intermediate solution representation with some set of production rules. To use this method, I would
have to define a grammar for haikus --- that is, find some way to deterministically turn a finite
array of discrete symbols into a haiku.

The other problem that I have to solve is that I will need to find a fitness function. This will
have to be done no matter what approach I take. I believe that it will likely have to be a
comparison of two haikus, rather than a strict numerical score between 0 and 1.
